Equalizer 2.0 --\\Convergence of a Parallel Rendering Framework

### 2017-11-30 paperIEEE.tex
RTNeuron section
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@64 db7c848b-7755-4df2-b763-8796797afa52

\subsection{RTNeuron}
\cite{HBBES:13}

>>>>

\subsection{RTNeuron}

RTNeuron \cite{HBBES:13} is a scalable real-time rendering tool for the
visualisation of neuronal simulations based on cable models. It is on
OpenSceneGraph for data management and Equalizer for parallel rendering, and
focuses not only on fast rendering times, but also on fast loading times with no
offline preprocessing. It provides level of detail (LOD) rendering, high quality
anti-aliasing based on jittered frusta and accumulation during still views,
interactive modification of the visual representation of neurons in a per-neuron
basis (full neuron vs. soma only, branch pruning depending on the branch level,
\dots). RTNeuron implements both sort-first and sort-last rendering with order
independent transparency.
